[dcpo_demsupport]

### 2020-06-12 paper/dcpo_demsupport.Rmd

```{r claassen_input}
claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen (note: these are his years right now)
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1996 | year==2001)) |
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2005)) |
              (country=="India") |
              (country=="Pakistan" & (year==1996 | year==2001)) |
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>% 
  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb471")) %>%  # surveys unused by Claassen
  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file

@@

supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
  read_csv(col_types = "cdcddcdc")

# Required by the replication file
p_load(
  countrycode,
  MASS,
  psych,
  arm,
  loo,
  rstanarm,
  RColorBrewer,
  devtools,
  dgo
)

library(MASS)
library(arm)
library(dplyr)
library(tidyr)
library(rstan)
library(loo)
library(ggplot2)
library(RColorBrewer)

>>>>

```{r claassen_input}
claassen_input_raw1 <- read_csv("data/claassen_input_raw.csv") %>% 
  filter(!(str_detect(item, "army") & # WVS obs identified as problematic by Claassen 
    ((country=="Albania" & year==1998) |
         (country=="Indonesia" & (year==2001 | year==2006)) |
         (country=="Iran" & year==2000) |
         (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
         (country=="Vietnam" & year==2001)) |
    (str_detect(item, "strong") &
         ((country=="Egypt" & year==2012) |
              (country=="Iran" & (year==2000 | year==2007)) | #in DCPO, the year is 2007 rather than 2005
              (country=="India") |
              (country=="Pakistan" & (year==1997 | year==2001)) | #in DCPO,it is 1997 instead of 1996
              (country=="Kyrgyzstan" & (year==2003 | year==2011)) |
              (country=="Romania" & (year==1998 | year==2005 | year==2012)) |
              (country=="Vietnam" & year==2001))))) %>% 
  filter(!(survey=="evs2017" | survey == "arabb5" | survey == "eb471")) %>%  # surveys unused by Claassen
  mutate(item = if_else(item == "strong_amb_1" & year == 2004, "strong_amb_2", item)) # items conflated in amb_combo file

@@

supdem <- get_file("supdem raw survey marginals.tab", "doi:10.7910/DVN/HWLW0J") %>% 
  read_csv(col_types = cols(.default = col_double(), 
                            Country = col_character(),
                            CAbb = col_character(),
                            Project = col_character()))

# Required by the replication file
library(MASS)
library(arm)
library(dplyr)
library(tidyr)
library(rstan)
library(loo)
library(ggplot2)
library(RColorBrewer)
